Temporality is Important for Networks of Hospital Patient Transfers

### 2025-01-15 reports/report.qmd
Add multichain hitting among other things

sns.set_theme(style='ticks')
sns.set_context('paper')
plt.style.use('tableau-colorblind10')
```

@@

```{python}
# simulation archives from run_zero*.py
simulation_archives = {
    'temporal': '../zero_sims/temporal/sim_all_30s.h5',
    'static': '../zero_sims/static/sim_all_30s.h5',
    'snapshot': '../zero_sims/snapshot/sims_with_30seeds_pseudocap.h5',
    'naive_static': '../zero_sims/naive_static/sim_all_30s.h5',
}

@@

# metrics precomputed in compute_summary_stats.ipynb
for label, archive in simulation_archives.items():
        processed_results[label] = pl.read_parquet(Path(archive).with_name('metrics_30s.parquet'))
```

>>>>

sns.set_theme(style='ticks')
sns.set_palette('colorblind')
sns.set_context('paper')
```

@@

```{python}
# simulation archives from run_zero*.py
simulation_archives = {
    'temporal': '../zero_sims/temporal/sim_all_30s.h5',
    'static': '../zero_sims/static/sim_all_30s_fixed_axis.h5',
    'snapshot': '../zero_sims/snapshot/sims_with_30seeds_pseudocap_fixed_axis.h5',
    'naive_static': '../zero_sims/naive_static/sim_all_30s.h5',
}

metrics_archives = {
    'temporal': '../zero_sims/temporal/metrics_30s.parquet',
    'static': '../zero_sims/static/metrics_30s_fa.parquet',
    'snapshot': '../zero_sims/snapshot/metrics_30s_fa.parquet',
    'naive_static': '../zero_sims/naive_static/metrics_30s.parquet'
}

@@

# metrics precomputed in compute_summary_stats.ipynb
for label, archive in metrics_archives.items():
        processed_results[label] = pl.read_parquet(archive)
```
